Library Parser

### 2024-10-04 studies/library_formatter.qmd
fix(site): fix links in qmd files
correct cross-referencing in library-parser, pass 3 comparison, and search syntax

```{r}
# read in bibtex library as data frame
bib_df_ca <- bib2df::bib2df('metaMER_library_third_pass_ca.bib')
bib_df_te <- bib2df::bib2df('metaMER_library_third_pass_te.bib')
bib_df_ca <- dplyr::filter(bib_df_ca,PRIORITY=='prio1')
bib_df_te <- dplyr::filter(bib_df_te,PRIORITY=='prio1')
sum(bib_df_ca$BIBTEXKEY %in% bib_df_te$BIBTEXKEY)==nrow(bib_df_ca)
```

>>>>

```{r}
# read in bibtex library as data frame
bib_df_ca <- bib2df::bib2df(paste0(here::here(),
                                   "/studies/bib/Passes/", 
                                   "metaMER_library_third_pass_ca.bib")
)
bib_df_te <- bib2df::bib2df(paste0(here::here(),
                                   "/studies/bib/Passes/", 
                                   "metaMER_library_third_pass_te.bib")
)
bib_df_ca <- dplyr::filter(bib_df_ca,PRIORITY=='prio1')
bib_df_te <- dplyr::filter(bib_df_te,PRIORITY=='prio1')
sum(bib_df_ca$BIBTEXKEY %in% bib_df_te$BIBTEXKEY)==nrow(bib_df_ca)
```

### 2024-10-04 studies/library_parser.qmd
fix(site): fix links in qmd files
correct cross-referencing in library-parser, pass 3 comparison, and search syntax

```{r}
eval(parse(text = meta_df$model_rate_emotion_values[22]))
```

@@

@@

Some studies include multiple bibtex fields for substudies/evaluations of different feature sets. E.g., `MODEL_RATE_EMOTION_VALUES_A` and `MODEL_RATE_EMOTION_VALUES_B`. We need to apply special operations to separate these values for further analysis.

```{r eval = F, echo = F}
## function to parse output of multiple models nested within a single cell
parse_model_output = function(df)
{ # loop across rows
  # apply function to replace NAs with empty string
  sapply(1:nrow(df), function(x) {
    df$model_rate_emotion_values <- tidyr::replace_na(df$model_rate_emotion_values, '') # detect cells with rbind in them
    if(str_count(df$model_rate_emotion_values[x], "rbind") > 1) {
      # match first model (name between first underscore and rbind)
      model_1_name <- str_match(df$model_rate_emotion_values[x], 
                                "(?<=_).*?(?=rbind)")
      # match subsequent models (name between MODEL_RATE_EMOTION_VALUES_ and rbind)
      model_names <- str_extract_all(df$model_rate_emotion_values[x], 
                                     "(?<=MODEL_RATE_EMOTION_VALUES_).*?(?=rbind)")
      # combine names
      model_names <- unlist(c(model_1_name, model_names))
      # remove special characters
      model_names <- gsub("[^[:alnum:]]", "", model_names)
      # get corresponding values for each model
      model_results <- str_split(df$model_rate_emotion_values[x], 
                "MODEL_RATE_EMOTION_VALUES")
      # get rid of everything up to "rbind"
      model_results <- lapply(model_results, function(x) str_remove(x, 
                                                          '.+?(?=rbind)'))
      # now unlist the models and give them names to add later
      model_results <- unlist(model_results)
       model_results <- paste(model_names, '=', model_results)
      names(model_results) <- model_names
     # return(model_results)
    }
    else { # otherwise, if dealing with non-listed, just return the existing value
      model_results <- df$model_rate_emotion_values[x]
    }
    return(model_results)
  }
    )
  # see whether rbind appears multiple times

@@

```{r}
this_study <- data.frame(citekey = c('testStudy2023ab','testStudy2023ab', 'testStudy2020of'),
  model_rate_emotion_values = c("rbind('marsyas.random forest.mfcc.msd.1' = c(valence_r2.mean = 0.9, arousal_r2.mean = 0.5,
                                  valence_r2.sd = 0.4, arousal_r2.sd = 0.3,
  valence_mse.mean = 0.3, arousal_mse.mean = 9.1),
  'random forest.mfcc.deam.1' = c(valence_r2.mean = 0.9, arousal_r2.mean = 0.5))",
  "rbind('librosa.linear regression.mfcc.ismir.1' = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3, valence_r2.sd = 0.2, arousal_r2.sd = 0.4,
  euclid_euclid.mean = 0.32, euclid_euclid.sd = 0.1))",
  "rbind('mirtoolbox.neural net.pitch.filmMusic.2' = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3))")
)
```

@@

```{r}
dplyr::tibble(get_study_summaries(this_study))
```

>>>>

```{r}
source(paste0(here::here(), "/R/format-study-results.R"))
eval(parse(text = meta_df$model_rate_emotion_values[22]))
```

@@

```{r eval = F, echo = F}

@@

# Some studies include multiple bibtex fields for 
# substudies/evaluations of different feature sets. E.g., 
# `MODEL_RATE_EMOTION_VALUES_A` and `MODEL_RATE_EMOTION_VALUES_B`. 
# We need to apply special operations to separate these values for 
# further analysis.

## function to parse output of multiple models nested within a single cell
parse_model_output = function(df)
{ # loop across rows
  # apply function to replace NAs with empty string
  sapply(1:nrow(df), function(x) {
    df$model_rate_emotion_values <- tidyr::replace_na(df$model_rate_emotion_values, '') # detect cells with rbind in them
    if(str_count(df$model_rate_emotion_values[x], "rbind") > 1) {
      # match first model (name between first underscore and rbind)
      model_1_name <- str_match(df$model_rate_emotion_values[x], 
                                "(?<=_).*?(?=rbind)")
      # match subsequent models (name between MODEL_RATE_EMOTION_VALUES_ and rbind)
      model_names <- str_extract_all(df$model_rate_emotion_values[x], 
                                     "(?<=MODEL_RATE_EMOTION_VALUES_).*?(?=rbind)")
      # combine names
      model_names <- unlist(c(model_1_name, model_names))
      # remove special characters
      model_names <- gsub("[^[:alnum:]]", "", model_names)
      # get corresponding values for each model
      model_results <- str_split(df$model_rate_emotion_values[x], 
                "MODEL_RATE_EMOTION_VALUES")
      # get rid of everything up to "rbind"
      model_results <- lapply(model_results, function(x) str_remove(x, 
                                                          '.+?(?=rbind)'))
      # now unlist the models and give them names to add later
      model_results <- unlist(model_results)
       model_results <- paste(model_names, '=', model_results)
      names(model_results) <- model_names
     # return(model_results)
    }
    else { # otherwise, if dealing with non-listed, just return the existing value
      model_results <- df$model_rate_emotion_values[x]
    }
    return(model_results)
  }
    )
  # see whether rbind appears multiple times

@@

```{r}
this_study <- data.frame(citekey = c('testStudy2023ab','testStudy2023ab', 'testStudy2020of'),
  model_rate_emotion_values = c("rbind('marsyas.random forest.mfcc.msd.1' = c(valence_r2.mean = 0.9, arousal_r2.mean = 0.5,
                                  valence_r2.sd = 0.4, arousal_r2.sd = 0.3,
  valence_mse.mean = 0.3, arousal_mse.mean = 9.1),
  'essentia.random forest.mfcc.deam.1' = c(valence_r2.mean = 0.9, arousal_r2.mean = 0.5))",
  "rbind('librosa.linear regression.mfcc.ismir.1' = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3, valence_r2.sd = 0.2, arousal_r2.sd = 0.4,
  euclid_euclid.mean = 0.32, euclid_euclid.sd = 0.1))",
  "rbind('mirtoolbox.neural net.pitch.filmMusic.2' = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3))")
)
```

@@

```{r}
dplyr::tibble(get_study_summaries(this_study)) |>
  knitr::kable()
```

### 2024-10-04 studies/search_syntax.qmd
fix(site): fix links in qmd files
correct cross-referencing in library-parser, pass 3 comparison, and search syntax

#### Read first pass data ---------------------
d <- bib2df("../studies/metaMER_library_first_pass_year_fixed.bib")
# Remove extra fields
d <- dplyr::select(d,-C1,-DATE.ADDED,-DATE.MODIFIED,-LA,-BDSK.URL.1,-BDSK.URL.2,-ISBN)
# Add explicit source
d$SOURCE[str_detect(d$UNIQUE.ID,'WOS')] <- 'Web of Science'
d$SOURCE[is.na(d$SOURCE)] <- 'Open Alex'
#print(knitr::kable(table(d$SOURCE)))

>>>>

#### Read first pass data ---------------------
d <- bib2df::bib2df(paste0(here::here(),
                                   "/studies/bib/Passes/", 
                                   "metaMER_library_first_pass.bib")
)
# Remove extra fields
d <- dplyr::select(d,-C1,-DATE.ADDED,-DATE.MODIFIED,-LA,-BDSK.URL.1,-BDSK.URL.2,-ISBN)
# Add explicit source
d$SOURCE[str_detect(d$UNIQUE.ID,'WOS')] <- 'Web of Science'
d$SOURCE[is.na(d$SOURCE)] <- 'Open Alex'
#print(knitr::kable(table(d$SOURCE)))
